Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-16 code/r2analysis.Rmd
finished r2 analysis

library(tidyverse)

@@

r2mod <- list()
r2val <- list()
ktval <- list()

for (i in 1:n_start) {
  r2mod[[i]] <- list()
  r2val[[i]] <- list()
  ktval[[i]] <- list()

  for (j in 1:n_stop) {
    r2mod[[i]][[j]] <- list()
    r2val[[i]][[j]] <- list()
    ktval[[i]][[j]] <- list()

@@

      r2mod[[i]][[j]][[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
      r2val[[i]][[j]][[k]] <- summary(r2mod[[i]][[j]][[k]])$r.squared
      ktval[[i]][[j]][[k]] <- -coef(r2mod[[i]][[j]][[k]])[2]

@@

```
PLOTS: 
```{r message=FALSE}

@@

r2final %>%
  group_by(start, stop) %>%
  summarise(mean_r2 = mean(r2)) %>%
  ggplot(aes(x = start, y = stop, fill = mean_r2, label = round(mean_r2,3))) +
  geom_tile() +
  geom_text() +
  scale_fill_viridis_c()

r2final %>%
  group_by(start, stop) %>%
  summarise(min_r2 = min(r2)) %>%
  ggplot(aes(x = start, y = stop, fill = min_r2, label = round(min_r2,3))) +
  geom_tile() +
  geom_text() +
  scale_fill_viridis_c()

>>>>

library(tidyverse)
library(cowplot)

@@

r2data <- list()
r2mod <- list()
r2val <- list()
ktval <- list()

for (i in 1:n_start) {
  r2data[[i]] <- list()
  r2mod[[i]] <- list()
  r2val[[i]] <- list()
  ktval[[i]] <- list()

  for (j in 1:n_stop) {
    r2data[[i]][[j]] <- list()
    r2mod[[i]][[j]] <- list()
    r2val[[i]][[j]] <- list()
    ktval[[i]][[j]] <- list()

@@

      r2data[[i]][[j]][[k]] <- tempdata
      r2mod[[i]][[j]][[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
      r2val[[i]][[j]][[k]] <- summary(r2mod[[i]][[j]][[k]])$r.squared
      ktval[[i]][[j]][[k]] <- -coef(r2mod[[i]][[j]][[k]])[2]

@@

CURVATURE (CRUDE) ANALYSIS:
```{r}

modresid <- list()
curvmod <- list()
curvval <- list()

for (i in 1:length(r2mod)) {
  modresid[[i]] <- list()
  curvmod[[i]] <- list()
  curvval[[i]] <- list()

  for (j in 1:length(r2mod[[i]])) {
    modresid[[i]][[j]] <- list()
    curvmod[[i]][[j]] <- list()

    for (k in 1:length(r2mod[[i]][[j]])){
      modresid[[i]][[j]][[k]] <- tibble(resid = resid(r2mod[[i]][[j]][[k]]),
                                        t = r2data[[i]][[j]][[k]]$t)
    }

    modresid[[i]][[j]] <- bind_rows(modresid[[i]][[j]])
    curvmod[[i]][[j]] <- lm(data = modresid[[i]][[j]], 
                            formula = resid ~ t + I(t^2))
    curvval[[i]][[j]] <- tibble(start = i, 
                                stop = j, 
                                curv = curvmod[[i]][[j]]$coefficients[3])
  }
}

PLOTS: 
```{r message=FALSE}

@@

p1 <- r2final %>%
  group_by(start, stop) %>%
  summarise(mean_r2 = mean(r2)) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = mean_r2, label = round(mean_r2,3))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
  labs(y = "Timesteps Removed from End of Run", 
       x = "Timesteps Removed from Beginning of Run", 
       fill = expression(paste("Mean ",R^{2})))

p2 <- r2final %>%
  group_by(start, stop) %>%
  summarise(min_r2 = min(r2)) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = min_r2, label = round(min_r2,3))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(midpoint = .5, limits = c(0,1)) +
  labs(y = "Timesteps Removed from End of Run", 
       x = "Timesteps Removed from Beginning of Run", 
       fill = expression(paste("Min. ",R^{2})))

p3 <- bind_rows(curvval) %>%
  ggplot(aes(x = as.factor(as.numeric(start)-1), y = as.factor(as.numeric(stop)-1), fill = curv, label = signif(curv, digits = 2))) +
  geom_tile() +
  geom_text() +
  scale_fill_gradient2(low = scales::muted("red"), mid = "white", high = scales::muted("red")) +
    labs(y = "Timesteps Removed from End of Run", 
       x = "Timesteps Removed from Beginning of Run", 
       fill = expression(paste(italic(t^{2})," Coefficient")))

final_plot <- plot_grid(p3, p1, p2, labels = c("(a)","(b)","(c)"), scale = .9)

final_plot
```
